\section{Project Experience in File and Storage Systems}

\cvitem{\bf Storage system design for AI applications}{2022 May. -- present}
\begin{itemize}
    \item {Designing storage-side acceleration for large-scale DL applications.}
    \item {\it\small(Recommendation Systems) }
\end{itemize}
%\begin{itemize}
%    \item {Storage system .}
%    \item {Studying performance of HBM in GPGPUs for data analytics workloads.}
%    \item {\it\small(CML, HBM, MLC, VTune, Spark, HiBench, BabelStream, HIP) }
%\end{itemize}

\cvitem{\bf Performance study of emerging memory technologies}{2022 Aug. -- 2023 May.}
\begin{itemize}
    \item {Analyzing performance impact of CXL memory expansion for data center workloads.}
    \item {Studying performance of HBM in GPGPUs for data analytics workloads.}
    \item {\it\small(CML, HBM, MLC, VTune, Spark, HiBench, BabelStream, HIP) }
\end{itemize}

\cvitem{\bf Reliable Elastic Data Service (RED)}{2021 Jul. -- 2022 Jul., DDN Storage}
\begin{itemize}
    \item {Developing components on core object IO path and metadata management.}
    \item {Developing a distributed object IO workload generation and testing framework.}
    \item {\it\small(Distributed Systems, Software Defined Storage, Object Storage, Kubernetes) }
\end{itemize}

\cvitem{\bf Scalable data infrastructure for science}{2019 -- 2021, Oak Ridge National Lab.}
\begin{itemize}
    \item {Developing a scientific data repository that allows data sharing among scientists.}
    \item {Developing a web portal that interacts with the backend storage.}
    \item {Deploying the services with containers on the OpenShift cluster.}
    \item {\it\small(Python, Django, PostgreSQL, OpenShift, Docker, Globus, DOI) }
\end{itemize}

\cvitem{\bf Metadata indexing framework for HPC archival storage systems}{2018 -- 2021,
Oak Ridge National Lab.}
\begin{itemize}
    \item {Developing a software framework that incrementally collects metadata from HPSS and builds data catalog.}
    \item {Developing a framework that extracts metadata from well-known document files without user intervention.}
    \item {Developing command-line utilities for system administrators and users.}
    \item {\it\small (HPSS, IBM DB2, PostgreSQL, Apache Tika, XDR, cURL, ElasticSearch, Kafka)}
\end{itemize}

\cvitem{\bf UnifyFS: A userspace checkpoint file system for HPC burst buffers}{2017 -- 2021, Oak Ridge National Lab.}
\begin{itemize}
    \item {Exascale Computing Project (ECP): Software technologies/Data and Visualization/ExaIO}
    \item {Developing an ephemeral distributed file system for node-local burst buffers
           to speed-up the application checkpoint in HPC systems.}
    \item {\it\small (FUSE, MPI, PMIx, MDHIM, LevelDB, Mercury, Margo, Argobots, Slurm, LSF)}
\end{itemize}

\cvitem{\bf Large-scale file system snapshot and workload analysis}{2016 -- 2019, Oak Ridge National Lab.}
\begin{itemize}
    \item {Analyzing the snapshot data of Spider II (32~PB Lustre) file system.}
    \item {Analyzing the eight year worth workloads of 80~PB HPSS archival storage system.}
    \item {\it\small (Lustre, HPSS, Spark, SparSQL, Parquet, Python, MySQL, SQLite)}
\end{itemize}

\cvitem{\bf File system-integrated search and discovery services for HPC}{2015 -- 2017, Oak Ridge National Lab.}
\begin{itemize}
    \item {Developing a file system-integrated metadata indexing framework that supports user-defined tagging.}
    \item {Prototyping the file system system using GlusterFS and CephFS.}
    \item {\it\small (GlusterFS, CephFS, Linux, SQLite, NetCDF)}
\end{itemize}

\cvitem{\bf Programming framework for processing-in-memory architecture}{2015 -- 2016, Oak Ridge National Lab.}
\begin{itemize}
    \item {Developing a programming library (C/C++) and a runtime framework
        that distributes data analysis tasks across an array of PIM devices.}
    \item {Developing a kernel device driver that emulates PIM devices in a NUMA architecture.}
    \item {\it\small(NUMA, Pthread, Intel TBB, Linux Kernel)}
\end{itemize}

\cvitem{\bf Analysis-aware storage system for HPC}{2013 -- 2015, Oak Ridge National Lab./Virginia Tech}
\begin{itemize}
    \item {Developing an active storage framework by extending the SCSI T10 OSD-2
        specification.}
    \item {Extending the Linux exofs file system to support the extended OSD protocol.}
    \item {Developing an active OSD target using the Linux TGT framework.}
    \item {Developing a FUSE file system that manages the array of active OSD devices.}
    \item {\it\small(Linux Kernel, SCSI T10 OSD-2 Protocol, Linux TGT, FUSE, SQLite)}
\end{itemize}

\cvitem{\bf Hierarchical multimedia data management in hybrid storage architecture}{2007 -- 2009, Hanyang University}
\begin{itemize}
    \item {Developing a content popularity analyzer that identifies
        popular media contents in a commercial media server.}
    \item{Developing a light-weight file system for storage class memory devices (PRAM) in media cache servers.}
    \item{\it\small(Linux Kernel, Windows Media Server)}
\end{itemize}

\cvitem{\bf Development of a transactional record storage for NAND flash memory}{2006 -- 2008, Hanyang University}
\begin{itemize}
    \item{Developing a flash-based DBMS atop Linux MTD to manage EPG data in a set-top box.}
    \item{Modifying a buffer management policy of PostgreSQL
        to generate an optimized IO sequence for flash memory.}
    \item{Developing an interactive framework that
        identifies a FTL mapping schema for NAND flash memory.}
    \item{\it\small(Linux Kernel, Linux MTD, Wisconsin Storage System, PostgreSQL,
        Linux blktrace, ARM-based embedded board)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other Project Experience}

\cvitem{\bf Development of a web-based social marketing game}{2011, Pitapat Mobile}
\begin{itemize}
    \item{Developing a web application that features social quiz games and
        integrating it to the Facebook using the Facebook API.}
    \item{Developing a mobile version game website.}
    \item{\it\small(C\#, Javascript, JQuery, CSS, HTML, REST, ASP.NET, SQL Server, Amazon EC2)}
\end{itemize}

\cvitem{\bf Development of an image transfer library for a self-driving vehicle}{2008, Metabuild co.}
\begin{itemize}
    \item {Developing a system library that transfers requested pixel data from the CMOS camera
        to a lane-recognition module for self-driving vehicles.}
    \item{\it\small(Linux, C, ARM-based embedded board)}
\end{itemize}

\cvitem{\bf Development of an online survey website}{Feb 2010, Aug 2009, Dept. of English Education, Hanyang University}
\begin{itemize}
    \item{Developing a web application that dynamically visualizes online survey results with graphs.}
    \item{\it\small(Linux, PHP, HTML, Javascript, MySQL, GD, Apache, Microsoft Excel)}
\end{itemize}

\cvitem{\bf Construction of a protein function database}{2006 -- 2008, Hanyang University}
\begin{itemize}
    \item {Developing a GUI environment for scientists to verify protein relation graphs
        that are automatically inferred from academic papers.}
    \item{\it\small(Windows, SQLServer, Delphi)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvitem{\bf Development of an online lesson website}{2002 -- 2003, Golfschool co.}
\begin{itemize}
    \item{Developing and maintaining a commercial company website with
        online sports lessons and an integrated shopping mall.}
    \item{\it\small(Linux, Apache, PHP, MySQL, HTML, Javascript)}
\end{itemize}
