\section{OTHER PROJECT EXPERIENCES} 
\vspace{0.03in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %\vspace{-0.15in}
  {\bf A Programming Framework for Processing-In-Memory Architecture}
   {\it \footnotesize --- 2015-2016, Oak Ridge National Lab.}
   \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
    \item[-] Developed a high-level programming interface (C/C++) and a runtime environment that
             facilitates data analysis tasks with an array of PIM devices.
%    \item[-] Developed a runtime system that optimizes the data placement across an array of
%             PIM devices.
    \item[-] Developed a kernel device driver that emulates PIM devices in a NUMA architecture.
    \item[] {\small(NUMA, Pthread, Intel TBB, Linux Kernel)}
   \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{-0.15in}
  {\bf Development of a Web-Based Social Marketing Game}
    {\it \footnotesize --- Jan-June 2011, Pitapat Mobile, S. Korea}
    \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
     \item[-] Developed a social quiz/marketing web application using 
              the Microsoft ASP.NET. %for desktop and mobile browsers.
     \item[-] Integrated the web application to the Facebook app platform using the Facebook API.
     \item[]  {\small(C\#, Javascript, JQuery, HTML, PHP, SQL Server, MySQL, Amazon EC2)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{-0.15in}
  {\bf Development of an Image Transfer Library for a Self-Driving Vehicle}
    {\it \footnotesize --- Dec 2008, Metabuild co., S. Korea}
    \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
     \item[-] Developed a userspace library that transfers requested pixel data
              from the CMOS camera
              to a lane-recognition module in a self-driving vehicle.
     \item[] {\small(Linux, C, ARM-based embedded board)}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{-0.15in}
{\bf Development of an Online Survey Website}
  {\it \footnotesize --- Feb 2010, Aug 2009, Dept. of English Education, Hanyang University}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
     \item[-] Developed an online-survey web application including administrative tools.
     \item[-] Developed a web application that visualizes interactions among educators.
     \item[] {\small(Linux, PHP, HTML, Javascript, MySQL, GD, Apache, Microsoft Excel)}
  \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{-0.15in}
  {\bf Construction of a Protein Function Database} 
    {\it \footnotesize --- 2006-2008, Database Lab., Hanyang University}
    \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
    \item[-] Developed a GUI environment that allows medical researchers to verify protein interaction graphs
             that are automatically extracted from academic articles.
    \item[] {\small(Windows, SQLServer, Delphi)}
    \end{itemize}

    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{-0.15in}
  {\bf Development of an Online Lesson Website}
    {\it \footnotesize --- 2002-2003, Golfschool co., S. Korea}
    \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.02in}
     \item[-] Developed and maintained a commercial company website that 
              serves online golf lessons and an online shopping mall of sporting goods.
     \item[]  {\small(Linux, Apache, PHP, MySQL, HTML, Javascript)}
    \end{itemize}
